Multi-Domain Adaptation in Neural Machine Translation with Dynamic Sampling Strategies

### 2021-05-12 2021/emnlp/auto_cl_mdmt.tex
with last todos

Most approaches to adaptive / dynamic data selection take inspiration from \citet{Bengio09curriculum}, where the notion of \emph{curriculum learning} (CL) is initially introduced. CL relies on the notion of ``easiness'' of a sample to schedule the presentation of the training data so that the easiest examples presented first and the hardest, last. CL has been shown to speed up learning. While the initial aim was to improve and speed up training, it has also proven useful for domain adaptive / multi-domain / multi-lingual MT, based on alternative definitions of ``easiness''.

@@

>>>>

Most approaches to adaptive / dynamic data selection take inspiration from \citet{Bengio09curriculum}, where the notion of \emph{curriculum learning} (CL) is initially introduced. CL relies on the notion of ``easyness'' of a sample to schedule the presentation of the training data so that the easiest examples presented first and the hardest, last. CL has been shown to speed up learning. While the initial aim was to improve and speed up training, it has also proven useful for domain adaptive / multi-domain / multi-lingual MT, based on alternative definitions of ``easiness''.\fyTodo{Ajouter Grave}

@@

\section{Conclusion and future work}
\fyTodo{Write conclusion}

Contribution : generic framework for several settings. // comparison of several dynamic strategies.

Future work:
slow down learning during warm up or normalize reward; handle large number of classes;} 
too much importance to the dev ? randomize ?
